Compositional Certified Resource Bounds

### 2014-06-30 paper/main.tex
minor update to abstract

  This paper describes a novel quantitative resource analysis
  framework that tackles these challenges for C programs.  The
  analysis framework consists of three parts.  First, the runtime
  resource consumption of programs is formalized with a parametric
  cost semantics for CompCert Clight.  Second, a quantitative Hoare
  logic that can be used for interactive bound development is
  implement and proved sound with respect to the cost semantics in the
  Coq Proof Assistant.  The logic is very expressive and a shallow
  embedding enables a derived bound to be any function that is
  definable in Coq.  Third, an automatic amortized resource analysis
  for C programs that computes derivations in the quantitative Hoare
  logic is developed and implemented.  It is the first automatic
  amortized analysis that can derive bounds that depend on negative
  integers and differences between numbers, which is crucial to handle
  typical systems code.  Both, the quantitative logic and the
  automatic amortized analysis are naturally compositional and can be
  combined to semi-automatically derive global resource bounds.

  The practicability of the analysis framework is demonstrated with an
  experimental evaluation.  The expressivity of the logic is
  demonstrated by manually deriving customized bounds that are
  tailored to specific algorithms.  A comparison of the automatic
  amortized analysis with other automatic tools on 30 challenging
  examples from the literature and open-source software shows that the
  derived constant factors in our bounds are often more precise.
\end{abstract}

>>>>

  This paper describes a novel quantitative resource analysis
  framework that tackles these challenges for C programs.  The
  analysis framework consists of three parts.  First, the runtime
  resource consumption of programs is formalized with a parametric
  cost semantics for CompCert Clight.  Second, a quantitative Hoare
  logic that can be used for interactive bound development is
  implement and proved sound with respect to the cost semantics in the
  Coq Proof Assistant.  The logic is very expressive and shallow
  embedding enables a derived bound to be any function that is
  definable in Coq.  Third, an automatic amortized resource analysis
  for C programs that computes derivations in the quantitative Hoare
  logic is developed and implemented.  It is the first automatic
  amortized analysis that can derive bounds that depend on negative
  integers or differences between numbers, which is crucial to handle
  typical systems code.  Both, the quantitative logic and the
  automatic amortized analysis are naturally compositional and can be
  combined to semi-automatically derive global resource bounds.

  The practicability of the analysis framework is demonstrated with an
  experimental evaluation.  The expressivity of the logic is
  demonstrated by manually deriving customized bounds that are
  tailored to specific algorithms.  A comparison of the automatic
  amortized analysis with other automatic tools on 30 challenging
  examples from the literature and open-source software shows that the
  derived bounds are often more precise.
\end{abstract}
